Clean 2015 Raw Data

### 2018-04-25 data-raw/README.Rmd
Cleanup data-raw README file
Update data.raw to include session_info
Add N treatment tibble
Create tibble for distribution with package and inclusion in paper as a table

if (!dir.exists("../data")) {
  dir.create("../data", recursive = TRUE)
}
```

@@

```{r}
# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)

@@

>>>>

```

@@

```{r}
# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)
# 4. Add column with number of days after inoculation (DAI)

@@

# Nitrogen management data

Create a `tibble` object of the N treatments for use in the paper as a table.

N_management <- tibble::tibble(
  `Nitrogen treatment` = character(),
  Year = integer(),
  `Total N (kg/ha)` = integer(),
  `Basal Application` = integer(),
  `Tillering Application` = integer(),
  `Panicle Initiation` = integer()
)

N_management <- tibble::add_row(N_management, `Nitrogen treatment` = c("N0",
  "N100",
  "N120",
  "N60",
  "N180"
))

N_management$Year <- c(
  2015,
  2015,
  2015,
  2016,
  2016
)

N_management$`Total N (kg/ha)` <- c(
  0,
  100,
  120,
  60,
  180
)

N_management$`Basal Application` <- c(
  0,
  60,
  60,
  30,
  60
)

N_management$`Tillering Application` <- c(
  0,
  20,
  30,
  30,
  60
)

N_management$`Panicle Initiation` <- c(
  0,
  20,
  30,
  0,
  60
)

N_management

devtools::use_data(N_management,
                   compress = "bzip2",
                   overwrite = TRUE)
```

# Colophon

```{r}
sessioninfo::session_info()
```
